This R Markdown document is made interactive using Shiny. For more information on authoring Shiny content in R Markdown documents, see [Shiny in R Markdown](http://rmarkdown.rstudio.com/authoring_shiny.html). 

## Inputs and outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. In this example we create a `numericInput` with the name "rows" and then refer to it's value via `input$rows` when generating output:

```{r, echo=FALSE}
numericInput("rows", "How many cars?", 5)

renderTable({
  head(cars, input$rows)
})
```

In this example the output code was wrapped in a call to `renderTable`. There are many other render functions in Shiny that can be used for plots, printed R output, and more. This example uses `renderPlot` to create dynamic plot output:

```{r, echo=FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)

renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)

  # draw the histogram with the specified number of bins
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

## Embedded applications

It's also possible to embed an entire Shiny application within an R Markdown document. There are two syntaxes for this: 

1) Defining the application inline using the `shinyApp` function; or

2) Referring to an external application directory using the `shinyAppDir` function.

This example uses an inline definition:

```{r, echo=FALSE}
shinyApp(
  
  ui = fluidPage(
    selectInput("region", "Region:", 
                choices = colnames(WorldPhones)),
    plotOutput("phonePlot")
  ),
  
  server = function(input, output) {
    output$phonePlot <- renderPlot({
      barplot(WorldPhones[,input$region]*1000, 
              ylab = "Number of Telephones", xlab = "Year")
    })
  },
  
  options = list(height = 500)
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

This example embeds a Shiny application defined in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note that in all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.


