This R Markdown document is made interactive using Shiny. For more information on authoring Shiny content in R Markdown documents, see [Shiny in R Markdown](http://rmarkdown.rstudio.com/authoring_shiny.html). 

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Applications

It's also possible to embed an entire Shiny application within an R Markdown document. There are two syntaxes for this: 

1) Defining the application inline using the `shinyApp` function; or

2) Referring to an external application directory using the `shinyAppDir` function.

This example uses an inline definition:

```{r, echo=FALSE}
shinyApp(
  
  ui = fluidPage(
    selectInput("region", "Region:", 
                choices = colnames(WorldPhones)),
    plotOutput("phonePlot")
  ),
  
  server = function(input, output) {
    output$phonePlot <- renderPlot({
      barplot(WorldPhones[,input$region]*1000, 
              ylab = "Number of Telephones", xlab = "Year")
    })
  },
  
  options = list(height = 500)
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

This example embeds a Shiny application defined in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note that in all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.


