## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interative Documents (Shiny Docs)](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Embedded Shiny Application

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/04_mpg", package="shiny"),
  options=list(
    width="100%", height=500
  )
)
```

## Summary

- The first slide illustrates including Shiny inputs and outputs directly within an R code chunk.
- The second slide demonstrates embedding a full Shiny application using the `shinyAppDir` function (referencing a directory that contains an existing Shiny application).
- You can also use the `shinyApp` function to define an application inline.



